The Astropy Project

### 2017-10-20 main.tex
fix

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
Central to the success of \astropy is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on an publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by a maintainer responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy has a mechanism to more formally propose
changes to the code management (e.g.~the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community consensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python programming language.

>>>>

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
Central to the success of \astropy is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by a maintainer responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy has a mechanism to more formally propose
changes to the code management (e.g.~the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community consensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python programming language.
